\documentclass[12pt,a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{xcolor}

\begin{document}

% Personal Details Table
\section*{Housemate(s) Details}
\begin{tabular}{|p{0.4\textwidth}|p{0.25\textwidth}|p{0.24\textwidth}|}
\hline
Full legal names & & \\ \hline
D.o.B. & & \\ \hline
Gender & & \\ \hline
Nationality & \\ \hline
Passport No. & \\ \hline
Visa Type & \\ \hline
Visa expires & \\ \hline
Highest Education & \\ \hline
Phone & \\ \hline
Email & \\ \hline
\end{tabular}

\vspace{1cm}

% Emergency Contact Table
\section*{Housemate(s) Emergency Contact}
\begin{tabular}{|p{0.3\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}|}
\hline
Emergency Contact person & & \\ \hline
Relation to you & & \\ \hline
Email & & \\ \hline
Phone & & \\ \hline
Address & & \\ \hline
\end{tabular}

\vspace{1cm}

% Employment Information Table
\section*{Housemate(s) Employment information}
\begin{tabular}{|p{0.3\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}|}
\hline
Your Employer & & \\ \hline
Your Occupation/Position & & \\ \hline
Address & & \\ \hline
Contact person's names & & \\ \hline
Title of Position & & \\ \hline
Email & & \\ \hline
Phone & & \\ \hline
\end{tabular}

\vspace{1cm}

\section*{TERMS and CONDITIONS}

\begin{enumerate}
\item This agreement is made between the current tenants and the \textbf{Housemate/s}. The \textbf{Housemate} is the person/s named on this agreement who shall rent a bedroom.

\item The rent is \textbf{NZ\$350} per week and is to be paid weekly in advance by the \textbf{Housemate} to the \textbf{Head Tenant}. The rent does not include any utility bill. A bond of a two week rent \textbf{NZ\$700} is payable to the \textbf{Head Tenant} on or before the signing of this agreement.

\item This agreement starts on Saturday, the 26th of May 2024.

\item This agreement can be terminated by 30 days notice given by either party in writing.

\item Should the \textbf{Housemate} choose to find a replacement, the replacement recommended by the \textbf{Housemate} must be approved by the \textbf{Head Tenant}.

\item The \textbf{Housemate} is responsible for all rent due until a replacement takes occupation of the room.

\item The shared utility bills will be split by the numbers of people who are stated on the agreements at the time being. The \textbf{Head Tenant} is responsible to calculate the bill sharing monthly. The \textbf{Housemate} agrees to pay the bills at their earliest convenience within a week.

\item The \textbf{Housemate} agrees that only the \textbf{Housemate/s} named on the agreement is to reside at the House. If the situation changed, any persons need to reside at the House, they must submit an application and go through the full vetting process. It is only with the consent of the \textbf{Head Tenant} that any new applicant will be added to the agreement as a \textbf{Housemate} and be allowed to reside at the House.

\item The \textbf{Housemate} agrees that the \textbf{Housemate} is to not cause or permit any interference with the reasonable peace privacy and comfort of other Housemates or any other person residing in the neighborhood.

\item CLEANLINESS TO THE HOUSE
    \begin{enumerate}[label=\alph*.]
    \item The \textbf{Head Tenant} shall make sure that the HOUSE is in a reasonably clean condition on the day on which is agreed that the \textbf{Housemate} shall enter into occupation of the HOUSE.
    
    \item \textbf{Housemate} agrees to keep the HOUSE reasonably clean condition during the period of the agreement by sharing the effort on cleaning the common areas, including dining, sitting, kitchen, bathroom, laundry, hallway, stairway, courtyard, as well as the common areas nearby the HOUSE.
    
    \item The \textbf{Housemate} agrees to keep all drains, sink wastes and sanitary appliances clear and free from obstruction, and to properly clean the bath, shower vanity and any amenities provide in the bathroom on a regular basis to avoid the build-up of calcium and hard to remove dirt, and to wipe up water spilled on the floor to prevent damage being done to the floor and subfloor. Otherwise, the \textbf{Housemate} will split the cost of professional House-cleaning monthly for the above.
    \end{enumerate}

\item DAMAGE and REPAIR of THE HOUSE
    \begin{enumerate}[label=\alph*.]
    \item The \textbf{Housemate} shall make sure that care is taken to avoid damaging the rented room and any common area.
    
    \item The \textbf{Housemate} must not remove any shared stuff from the HOUSE that do not belong to the \textbf{Housemate}.
    
    \item The \textbf{Housemate} shall not do or allow anything to be done which would invalidate any insurance policy on the House or increase the premium and the \textbf{Housemate} shall pay the \textbf{Head Tenant} all increased premiums and all other expenses incurred because of any breach of this term.
    
    \item The \textbf{Housemate} agrees that \textbf{Housemate} or their guests carelessly damage a chattel or a part of the House, they are liable for the cost of the damage up to four weeks' rent or the insurance excess (if applicable), whichever is lower. Such as a result of accidental breakage of glass/mirror, toilet bowls, and washbasins in the House where the damage has been caused by the \textbf{Housemate}.
    
    \item The \textbf{Housemate} is advised that it is in the \textbf{Housemate}'s best interest to ensure that the \textbf{Housemate} has his own contents and chattels insurance including all risk liability due to the \textbf{Housemate}'s not being able to claim for any damages to their possessions on the \textbf{HOUSE owner}'s Insurance cover.
    \end{enumerate}

\item INSPECTION OF THE HOUSE
    \begin{enumerate}[label=\alph*.]
    \item The \textbf{Housemate} acknowledges the \textbf{Head Tenant}'s responsibility to conduct regular inspections to the HOUSE in order to identify and report any issues to the HOUSE owner. The \textbf{Head Tenant} has the right to inspect the property (including \textbf{Housemate}'s room) no more than once every 6 weeks, providing 48 hours' notice has been given by the \textbf{Head Tenant} or 24 hours' notice by a tradesman arranged by the \textbf{House owner} carrying out necessary maintenance.
    
    \item The \textbf{Housemate} acknowledges that photographs or videos will be taken to record the condition of the HOUSE. The \textbf{Housemate} agrees to move or cover any personal effects that might be photographed. If the \textbf{Housemate} fails to move or cover any items, then \textbf{Housemate} agrees to those items being included in any photographic record.
    
    \item The \textbf{Housemate} understands that \textbf{Housemate} must vacate on or before the \textbf{End Date}. The final inspection should be on the day of the \textbf{Housemate} moving out. The \textbf{Housemate} agrees to clear and clean the rented room and all common areas, and push out the rubbish bins.
    \end{enumerate}

\item VACATION OF THE HOUSE
    \begin{enumerate}[label=\alph*.]
    \item \textbf{Housemate} is bound to pay rent up to the end no matter the \textbf{Housemate} leave before or on the end date.
    
    \item At the end of this agreement, after the satisfactory inspection, the \textbf{Head Tenant} will return the bond after deducting NZD200 on-hold for the upcoming bills to the \textbf{Housemate}. The balance, after deducting the upcoming bills from the NZD200, will be returned to the \textbf{Housemate} within one month after the end date of the agreement or the satisfactory inspection whichever is later. The \textbf{Head Tenant} can deduct from the bond for any cost of cleaning fee, damages or loses which is the \textbf{Housemate}'s liability.
    \end{enumerate}
\end{enumerate}

\vspace{2cm}
\noindent\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\
Head Tenant Signature & Date \\[1cm]
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\
Housemate Signature & Date \\[1cm]
\rule{8cm}{0.4pt} & \rule{8cm}{0.4pt} \\
Housemate Signature (if applicable) & Date \\
\end{tabular}

\end{document}
